### 2017-02-26 2017mergingmerges/section/03-Definition.tex
Shifting figs around

\clearpage{}
% -----------------------------------------------------------------------------
\section{Process definitions}

\input{figures/ProcessDef.tex}

@@

The judgment form for feeding is $\ProcsFeed{\ti{inputs}}{\ti{network}}{\ti{streams}}{\ti{network}'}$.
The input map $\ti{inputs}$ contains values for the network inputs: network outputs are not allowed, but ignored channels can have values.
The result $\ti{streams}$ contains the original inputs as well as accumulated output values.
Feeding evaluates the process network until all input values have been injected.

>>>>

\clearpage{}
% -----------------------------------------------------------------------------
\section{Process definitions}
\input{figures/ProcessDef.tex}

@@

A judgment of the form $\ProcsFeed{cvs}{ps}{cvs'}{ps'}$ reads ``with channel values $cvs$, process group $ps$ takes a step and produces new channel values $cvs'$ and group $ps'$''. The channel values $cvs$ map channel names to a list of values. For input channels of the overall group, we initialize the map to contain a list of input values for each channel. For output channels of the overall group, values pushed to those channels are also collected in the same channel map. In a concrete implementation the input and output values would be transported over some IO device, but the simplified semantics here is sufficient to describe the abstract behavior of our system.
